Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples utilisables par Isabelle et Coq'' (CUIC). }

### 2016-01-21 ijcar2016/body.tex
use a description rather than a table

Nunchaku parses and types the input problem before applying a sequence
of translations, each reducing the distance to the target fragment. Here,
for instance, the coinductive predicates
\verb!even! and \verb!odd! are \emph{polarized} (specialized into
\verb!even+!, used only in positive positions, and \verb!even-! used in negative
positions),
$m$ is Skolemized into a fresh constants,
then then translated into admissible functions
before another pass uses the encoding from Section~\ref{sec:encoding}.
If a model is found, it is translated back to the input language.
Conceptually, the sequence of transformation is a \emph{two ways pipeline}
built by composing pairs \textsf{(encode,decode)}.
For each such pair, \textsf{encode}
transforms a problem over a signature $\Sigma$ in a logic
$\mathcal{L}$ to a problem over a signature $\Sigma'$ in a slightly different
logic $\mathcal{L}'$, and \textsf{decode} translates a model of \mathcal{L'}
over $\Sigma'$ into a model of $\mathcal{L}$ over $\Sigma$. The table
from Figure~\ref{fig:pipeline} presents the current pipeline implemented in Nunchaku.

\begin{figure}[tb]
%{{{
\begin{tabular}{|l|p{0.6\textwidth}|}
  \hline
  component & description \\
  \hline
  \hline
  Type inference
    & Infer types and checks definitions \\
  \hline
  Type skolemization
    & Replaces $\exists \alpha. p[\alpha]$
      with $p[\tau]$ where $\tau$ is a fresh type \\
  \hline
  Monomorphization
    & specializes polymorphic functions on their type arguments \\
  \hline
  Elimination of Equations
    & Translates multiple-equations definitions of functions into
      a single nested pattern matching \\
  \hline
  Polarization
    & specialize some predicates into a version used in positive position
      and one used in negative position \\
  \hline
  Unrolling
    & Add a decreasing argument to non-well-founded predicates \\
  \hline
  Skolemization
    & Introduce Skolem symbols for term variables \\
  \hline
  Elimination of Predicates
    & Changes a multi-clauses (co)inductive predicate definition
      into a single recursive function \\
  \hline
  Recursion Elimination
    & The encoding from Section~\ref{sec:encoding} \\
  \hline
  Elimination of Match
    & Transforms pattern-matching expressions into tests and selectors \\
  \hline
  CVC4 Invocation 
    & Call CVC4 to obtain a model \\
  \hline
\end{tabular}
%}}}
\caption{Pipeline of Transformations in Nunchaku}
\label{fig:pipeline}
\end{figure}

>>>>

Nunchaku parses and types the input problem before applying a sequence
of translations, each reducing the distance to the target fragment. Here,
for instance, the coinductive predicates
\verb!even! and \verb!odd! are \emph{polarized} (specialized into
\verb!even+!, used only in positive positions, and \verb!even-! used in negative
positions),
$m$ is Skolemized into a fresh constants,
then then translated into admissible functions
before another pass uses the encoding from Section~\ref{sec:encoding}.
If a model is found, it is translated back to the input language.
Conceptually, the sequence of transformation is a \emph{two ways pipeline}
built by composing pairs \textsf{(encode,decode)}.
For each such pair, \textsf{encode}
transforms a problem over a signature $\Sigma$ in a logic
$\mathcal{L}$ to a problem over a signature $\Sigma'$ in a slightly different
logic $\mathcal{L}'$, and \textsf{decode} translates a model of \mathcal{L'}
over $\Sigma'$ into a model of $\mathcal{L}$ over $\Sigma$. The pipeline
currently implemented in Nunchaku is described below.

\begin{description}
%{{{
  \item[Type inference] infers types and checks definitions;
  \item[Type skolemization]
    replaces $\exists \alpha. p[\alpha]$
      with $p[\tau]$ where $\tau$ is a fresh type;
  \item[Monomorphization]
    specializes polymorphic functions on their type arguments;
  \item[Elimination of Equations]
    translates multiple-equations definitions of functions into
      a single nested pattern matching;
  \item[Polarization]
    specializes some predicates into a version used in positive position
      and one used in negative position;
  \item[Unrolling]
    adds a decreasing argument to non-well-founded predicates;
  \item[Skolemization]
    introduces Skolem symbols for term variables;
  \item[Elimination of Predicates]
    changes a multi-clauses (co)inductive predicate definition
      into a single recursive function;
  \item[Recursion Elimination]
    performs the encoding from Section~\ref{sec:encoding};
  \item[Elimination of Match]
    transforms pattern-matching expressions into tests and selectors;
  \item[CVC4 Invocation] calls CVC4 to obtain a model.
%}}}
\end{description}
